### 2014-11-04 paper/experiments.tex
adding some fixes

\section{Experiments}

We conducted several performance tests to measure the throughput and scalability of our system. All these tests were performed on a LAN system called Lattice which has a network bandwidth of 1 Gbps. All nodes are Intel(R) Xeon(R) 2.4GHz 4 core duo machines with 1 GB of memory. We used Apache S4 0.6.0 version and Apache storm 0.9.2 version. Sample code used for all tests can be found here\cite{solutionCode}.

\subsection{Inter node communication}
We used a graph as shown in Figure \ref{ecgGraph} to process ECG signal data. Our solution \textit{EventProducer} and Yahoo S4\cite{neumeyer2010s4} \textit{EventProducer} read a file containing over 7500000 ECG records and push events with multiple threads. Twitter Storm\cite{twitterStorm} does not allow user threads to push data. So we used the \textit{spout} thread to send messages into the system. \textit{EventReceiver}  receives the ECG events, processes them and calculates heart rate interval periodically.  
\subsubsection{Throughput}
We executed our system with 1, 2 and 4  \textit{EventReceivers} for each system and measured the throughput, load average and network bandwidth for each case. Throughput was measured at the \textit{EventProducer} by calculating the total time required to send messages and the total number of messages send. Load average and network bandwidth were measured using top and atop linux commands respectively. Figure \ref{throuput} shows the throughput variation with the number of nodes for all systems.

@@

As shown in the Figure \ref{throuput}, our solution outperforms Twitter storm\cite{twitterStorm} and Yahoo S4\cite{neumeyer2010s4}. However by looking at the Figure \ref{throuput}, one might think even our solution is not scalable although it performs high. In order to examine the reason behind this, we looked into the network bandwidth and CPU load average values.

@@

\begin{figure*}[!t]
	\centering
	\subfloat[Network Usage]{\includegraphics[width=3.0in]{network.png}}
	\hfil
	\subfloat[CPU Load Average]{\includegraphics[width=3.0in]{loadaverage.png}}
	\caption{Network usage and CPU Load Average of the System}
	\label{networkandload}
\end{figure*}

By looking at the graphs, first it can be observed that our solution utilities all available network bandwidth (98\%) even with two receivers. In only one receiver case, high CPU load average at receiver indicates it has utilized available CPU power. Adding two receivers has increased the CPU power at receiving side utilizing all available network bandwidth. Therefore it can not increase the throughput without increasing network bandwidth although more CPU power is available at receiver nodes. Having more receiver nodes, we can observe that network bandwidth and CPU load average is reduced at each receiver, since load is shared among the receivers. However for other two systems, it neither hits the maximum network bandwidth available nor the full CPU power available at any stage. If a system does not make use of the available resources then adding more resources won't scale up the system. As explained in earlier, our solution utilities all available resources by using parallel TCP connections and having an efficient 
message converting technique.

@@

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{efficiency.png}

        \caption{Efficiency of Message Serialization}
        \label{efficiency}
\end{figure}

As shown in the figure \ref{efficiency}, Twitter storm\cite{twitterStorm} uses a minimum over head while Yahoo S4\cite{neumeyer2010s4} performs badly compared to other two. This overhead is due to its usage of java serialization. Then we analyzed for what our solution spends extra 32 bytes. Our solution adds a sequence number (an integer), receiving process id (a 8 byte string for this scenario), sending process id (a 8 byte string for this scenario) to order messages, dispatch the message to correct process and to parse the message at the server. Altogether it adds 26 (serialization format of a string uses two more bytes to keep the string length) extra bytes to each message at application level and another 4 bytes due to TCP overhead. This is the trade off we had to pay to improve the parallelism compared to direct one TCP communication per process.

\subsubsection{Latency}
We examined the message latency between the event producer and receiver. For this experiment, we sent the timestamp at the producer along the message and calculated the latency at the receiver. We took 6000 samples over the experiment duration. As shown in the figure \ref{latancydis}, we could observe the mean latency of 185.05 with the 95\% confidence interval of (182.56, 187.54).

\begin{figure*}[!t]
        \centering
        \subfloat[Histogram]{\includegraphics[width=3.0in]{latencyHistogram.png}}
        \hfil
        \subfloat[Box Plot]{\includegraphics[width=3.0in]{latencyBoxPlot.png}}
        \caption{Message Latency Distribution}
        \label{latancydis}
\end{figure*}

\subsection{Scalability}
We performed a scalability test for our system using the 3 level graph shown in Figure \ref{multigraph}. The processing data as well as the processing logic were obtained from the grand challenge problem of 8th ACM international conference on distributed event based systems. We used the publicly available 500MB of data to generate the events.

@@

This application predicts load averages using previous values and a machine learning algorithm. We implemented this logic using nodes as shown in the Figure \ref{multigraph}. First producer reads the data file and sends events to the \textit{avgCal} node which calculates the last minute average and sends the same event to both \textit{plugPredict} and \textit{housePredict} processors. Both \textit{plugPredict} and \textit{housePredict} processors predict the next values and send events to receivers. The original problem only requires to send those prediction events in 30s intervals. But we used a prediction event for each messages to observe how the system works with high load.

As in the earlier case, we conducted our experiments using one producer and multiplying the other processing nodes by 1, 2 and 4 times to measure the throughput increase at the producer. We ran each node in a separate machine so that our receiver configurations used 5, 10, 15 machines respectively. We measured the throughput,  network bandwidth and the CPU load average at the producer to examine the scalability of the system. Since the one receiver unit throughput greater than that of the storm one node scenario, we only used our system for this experiment.  Results are shown in the Figure \ref{scalability}.

@@

For one receiver unit case, we observed very high load average and network bandwidth usage at \textit{avgCal} node since it sends messages to two nodes. Then as shown in the figure \ref{scalability}, we could linearly scale up the system by adding more receiver units to add more cpu power to the system. When increasing the receiver units, we could observe throughput of the system increases proportional to number of receiving units. CPU load average of 13 at the producer indicates it has utilized all available CPU power and it is required to add more producers to scale this system further up.

>>>>

\section{Performance Benchmarks}

We conducted several performance tests to measure the throughput and scalability of our system. All these tests were performed on a LAN system called Lattice which has a network bandwidth of 1 Gbps. All nodes are Intel(R) Xeon(R) 2.4GHz 4 core duo machines with 16 GB of memory. We used Apache S4 0.6.0 version and Apache storm 0.9.2 version. Sample code used for all tests can be found here\cite{solutionCode}.

\subsection{Inter node communication}
We used a graph as shown in Figure \ref{ecgGraph} to process ECG signal data. Our solution \textit{EventProducer} and Yahoo S4\cite{neumeyer2010s4} \textit{EventProducer} read a file containing over 7500000 ECG records and push events with multiple threads. Twitter Storm\cite{twitterStorm} does not allow user threads to push data. So we used the \textit{spout} thread to send messages into the system. \textit{EventReceiver}  receives the ECG events, processes them and calculates heart rate interval periodically.

\subsubsection{Throughput}
We executed our system with 1, 2 and 4  \textit{EventReceivers} for each system and measured the throughput, load average and network bandwidth for each case. Throughput was measured at the \textit{EventProducer} by calculating the total time required to send messages and the total number of messages send. Load average and network bandwidth were measured using top and atop linux commands respectively. Figure \ref{throuput} shows the throughput variation with the number of nodes for all systems.

@@

As shown in the Figure \ref{throuput}, our solution outperforms Twitter Storm \cite{twitterStorm} and Yahoo S4 \cite{neumeyer2010s4}. However by looking at the Figure \ref{throuput}, one might think even our solution is not scalable although it performs well. In order to examine the reason behind this, we looked into the network bandwidth and CPU load average values.

@@

\begin{figure*}[!t]
	\centering
	\subfloat[Network Usage]{\includegraphics[width=3.0in]{network.png}}
	\subfloat[CPU Load Average]{\includegraphics[width=3.0in]{loadaverage.png}}
	\caption{Network usage and CPU Load Average of the System}
	\label{networkandload}
\end{figure*}

By looking at the graphs, first it can be observed that our solution utilities all available network bandwidth (98\%) even with two receivers. In the one receiver case, high CPU load average at the receiver indicates that it has utilized available CPU power. Adding two receivers has increased the CPU power at receiving side utilizing all available network bandwidth. Therefore, we can not increase the throughput without increasing network bandwidth although more CPU capacity is available at the receiver nodes. Having more receiver nodes, we can observe that network bandwidth and CPU load average is reduced at each receiver, since load is shared among the receivers. However for other two systems, it neither hits the maximum network bandwidth available nor the full CPU power available at any stage. If a system does not make efficient use of the available resources then adding more resources will not scale up the system. As explained in earlier, our solution utilities all available resources by using parallel TCP connections and having efficient message transformations.

@@

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{efficiency.png}
        \caption{Efficiency of Message Serialization}
        \label{efficiency}
\end{figure}

As shown in the figure \ref{efficiency}, Twitter Storm \cite{twitterStorm} uses a minimum over head while Yahoo S4 \cite{neumeyer2010s4} performs worse compared to other two. This overhead is due to its usage of Java serialization. We analyzed our solutions' extra overhead of 32 bytes. Our solution adds a sequence number (an integer), receiving process id (a 8 byte string for this scenario), sending process id (a 8 byte string for this scenario) to order messages, dispatch the message to correct process, and to parse the message at the server. Altogether it adds 26 (serialization format of a string uses two more bytes to keep the string length) extra bytes including 2 overhead bytes for streamID, to each message at application level and another 4 bytes due to TCP overhead. This is the trade off we had to pay to improve the parallelism compared to direct one TCP communication per process.

\subsubsection{Latency}
We examined the message latency between the event producer and receiver. For this experiment, we sent the timestamp at the producer along the message and calculated the latency at the receiver. We took 6000 samples over the experiment duration. As shown in the figure \ref{latancydis}, we could observe the mean latency of 185.05ms with the 95\% confidence interval of (182.56ms, 187.54ms).

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{latencyHistogram.png}
        \caption{Message Latency Distribution}
        \label{latancydis}
\end{figure}

\subsection{Scalability}
We performed a scalability test for our system using the 3-level graph shown in Figure \ref{multigraph}. The data as well as the processing logic were obtained from the Grand Challenge problem at 8th ACM International Conference on Distributed Event Based Systems. We used the publicly available 500MB of data to generate the events.

@@

This application predicts load averages using previous values and a machine learning algorithm. We implemented this logic using nodes as shown in the Figure \ref{multigraph}. The first producer reads the data file and sends events to the \textit{avgCal} node which calculates the last minute average and sends the same event to both \textit{plugPredict} and \textit{housePredict} processors. Both \textit{plugPredict} and \textit{housePredict} processors predict the next values and send events to receivers. The original problem only requires to send those prediction events in 30s intervals. But we used a prediction event for each messages to observe how the system works with high load.

As in the earlier case, we conducted our experiments using one producer and incrementing the other processing nodes by 1, 2 and 4 times to measure the throughput increase at the producer. We ran each node in a separate machine so that our receiver configurations used 5, 10, 15 machines respectively. We measured the throughput,  network bandwidth and the CPU load average at the producer to examine the scalability of the system. Since the one receiver unit throughput is greater than that of the Twitter Storm one node scenario, we only used our system for this experiment.  Results are shown in the Figure \ref{scalability}.

@@

For one the receiver unit case, we observed very high load average and network bandwidth usage at \textit{avgCal} node since it sends messages to two nodes. As shown in  Figure \ref{scalability}, we could linearly scale up the system by adding more receiver units to add more cpu power to the system. When increasing the receiver units, we could observe throughput of the system increases proportional to number of receiving units. Our CPU load average of 13 at the producer indicates it has utilized all available CPU power and it is required to add more producers to scale this system further up.

### 2014-11-04 paper/relatedwork.tex
adding some fixes

\section{Related Work}
Much of the inspiration for stream processing systems can be trace back to data stream management systems. These systems support a window based query language. Most of these languages are derived from SQL, for instance STREAM\cite{arasu2004stream} defines a language called \textit{Continuous Query Language(CQL)} which has similar syntactic characteristics as SQL. Aurora\cite{abadi2003aurora}, STREAM\cite{arasu2004stream} and Nile\cite{hammad2004nile} are some of the prominent implementations of DSMSs. Complex event processing(CEP) systems such as Esper\cite{esper}, Siddhi\cite{suhothayan2011siddhi}, Cayuga\cite{brenna2007cayuga} also share many characteristics with DSMSs except for their use cases. CEP systems are capable of handling multiple incoming event streams(which are similar to the input streams) and identifying patterns across streams which are of interest to the end users. However these systems do not support user defined logic and hence not suitable for implement complex logic based on machine 
learning techniques.

MapReduce\cite{dean2008mapreduce} is a widely adapted technology to process batch data with the popularity of Apache Hadoop\cite{hadoop}. In a MapReduce environment a problem is partitioned into smaller parts identified by a key and process parallely. Although these systems support user defined functions, data processing flow of these systems are fixed. Ciel\cite{murray2011ciel} address this problem by dynamically generating data flow graph. Since all these systems communicate through file system they inherently not suitable for real time processing\cite{lam2012muppet}.

Stream Processing Core (SPC)\cite{Amini2006}, Yahoo S4\cite{neumeyer2010s4} and Twitter Storm\cite{twitterStorm} address the above issue by supporting direct communication. These systems are based on the Actor model\cite{agha1985actors} and each system has a notion of processing element or computation. Processing Elements are used to perform user defined logic on the receiving events and emit newly generated events to other processing elements. In addition to basic communication these systems provide fault tolerance features such as reliable message delivery and dynamic membership management. However most of these systems do not focus on improving inter node communication performance.

Spark\cite{zaharia2010spark} introduces its RRDs\cite{zaharia2012resilient} to achieve better fault tolerance by storing the operations and replaying them instead of replicating data itself or use checkpointing to store data periodically. Spark Streaming\cite{zaharia2013discretized} extends this concept to distributed stream processing with the concept of discretized events. Spark streaming\cite{zaharia2013discretized} processes data as batches while storing them as RDDs \cite{zaharia2012resilient} to achieve higher throughput. This batch processing may introduce latencies which are not acceptable for some applications. Further it is not clear how to implement complex event processing algorithms such as we use our benchmarks with Spark Streaming. MillWheel\cite{akidau2013millwheel} is the stream processing system used at Google to process web queries. MillWheel\cite{akidau2013millwheel} provides reliable message processing as well as state persistence for its graph based computations. Unlike in our system 
MillWheel treat messages as binary 
messages leaving message parsing and serialization to application layer.

>>>>

\section{Related Work}
Much of the inspiration for stream processing systems can be trace back to data stream management systems. These systems support a window based query language. Most of these languages are derived from SQL, for instance STREAM \cite{arasu2004stream} defines a language called \textit{Continuous Query Language(CQL)} which has similar syntactic characteristics as SQL. Aurora \cite{abadi2003aurora}, STREAM \cite{arasu2004stream} and Nile \cite{hammad2004nile} are some of the prominent implementations of DSMSs. Complex event processing(CEP) systems such as Esper \cite{esper}, Siddhi \cite{suhothayan2011siddhi}, Cayuga \cite{brenna2007cayuga} also share many characteristics with DSMSs except for their use cases. CEP systems are capable of handling multiple incoming event streams(which are similar to the input streams) and identifying patterns across streams which are of interest to the end users. However these systems do not support user defined logic and hence not suitable for implement complex logic based on machine learning techniques.

MapReduce \cite{dean2008mapreduce} is a widely used to process batch data. Apache Hadoop \cite{hadoop} is a widely used implementation of MapReduce. In a MapReduce environment a problem is partitioned into smaller parts identified by a key and process parallely. Although these systems support user defined functions, data processing flow of these systems are fixed. Ciel \cite{murray2011ciel} address this problem by dynamically generating data flow graph. Since all these systems communicate through file system they inherently not suitable for real time processing \cite{lam2012muppet}.

Stream Processing Core (SPC) \cite{Amini2006}, Yahoo S4 \cite{neumeyer2010s4} and Twitter Storm \cite{twitterStorm} address the above issue by supporting direct communication. These systems are based on the Actor model \cite{agha1985actors} and each system has a notion of processing element or computation. Processing Elements are used to perform user defined logic on the receiving events and emit newly generated events to other processing elements. In addition to basic communication these systems provide fault tolerance features such as reliable message delivery and dynamic membership management. However most of these systems do not focus on improving inter node communication performance.

Spark \cite{zaharia2010spark} introduces its RRDs \cite{zaharia2012resilient} to achieve better fault tolerance by storing the operations and replaying them instead of replicating data itself or use checkpointing to store data periodically. Spark Streaming \cite{zaharia2013discretized} extends this concept to distributed stream processing with the concept of discretized events. Spark streaming \cite{zaharia2013discretized} processes data as batches while storing them as RDDs \cite{zaharia2012resilient} to achieve higher throughput. This batch processing may introduce latencies which are not acceptable for some applications. Further it is not clear how to implement complex event processing algorithms such as we use our benchmarks with Spark Streaming. MillWheel \cite{akidau2013millwheel} is the stream processing system used at Google to process web queries. MillWheel \cite{akidau2013millwheel} provides reliable message processing as well as state persistence for its graph based computations. Unlike our system, MillWheel treats messages as binary messages leaving message parsing and serialization to the application layer.

### 2014-11-04 paper/system_architecture.tex
adding some fixes

\section{System Design}
In this section we elaborate the underlying system design which is capable of processing 2.4 million messages per second. We emphasize three features of this design. Firstly between any two nodes there is a set of TCP connections (typically 20 connections)  to send messages. All processes share the same set of connections which we called the bridge. The advantage of this approach compared to having TCP connections per process is that it utilizes all available bandwidth even there is only one process per node. However since this is a common bridge now we have to send the receiving process id to dispatch the message, sending  process id to parse the message and sequence number to order messages. As we discuss later our experiments show that this approach perform several times better than the other systems despite the above overhead. Secondly we have implemented \textit{OutputStream} and \textit{InputStream} interfaces on top of java non blocking I/O API. Using these input and output streams we provide \textit{DataOutput} and \textit{DataInput} APIs to directly 
serialize message data to binary format without sending any metadata along the message. Finally except messages themselves, all the other objects used to serialize and parse the messages and parse the messages are not created at message processing time. All these objects are created when a process sends the first message and it is a one-time cost. Rest of this section further explains the design techniques we used to realize these concepts.
\subsection{Inter Process Communication}
Figure \ref{interprocess} shows the design involved in sending a message from one process to another. Lets assume there is a message at a client side process and that process wants to send this message to another process. First the client process sends this message to its \textit{ElementContainer}. \textit{ElementContainer} holds all the streams (this is an abstraction of a link in the process graph) to which this message needs to send and it push the message to all streams. Stream decides which node to send this message and passes the message along the target node details to \textit{ConnectionManager} which holds \textit{ClientConnection}s for each node. \textit{ConnectionManager} sends message to correct \textit{ClientConnection} using target node. \textit{ClientConnection} picks an available \textit{DataOutput} from its pool of \textit{DataOutputs} and invokes the serialize method of the message to send that to server side.

>>>>

\section{System Design}
In this section we elaborate on our underlying system that is capable of processing 2.4 million messages per second. We emphasize three features of this design. Firstly between any two nodes there is a set of TCP connections to send messages. All processes share the same set of connections, which we cumulatively call the bridge. The advantage of this approach compared to having TCP connections per process is that it utilizes all available bandwidth even there is only one process per node. However since this is a common bridge now we have to send the receiving process id to dispatch the message, sending  process id to parse the message and sequence number to order messages. As we discuss later our experiments show that this approach perform several times better than the other systems despite the above overhead. Secondly we have implemented \textit{OutputStream} and \textit{InputStream} interfaces on top of java non blocking I/O API. Using these input and output streams we provide \textit{DataOutput} and \textit{DataInput} APIs to directly 
serialize message data to binary format without sending any metadata along the message. Finally except messages themselves, all the other objects used to serialize and parse the messages and parse the messages are not created at message processing time. All these objects are created when a process sends the first message and it is a one-time cost. Rest of this section further explains the design techniques we used to realize these concepts.
\subsection{Inter Process Communication}
Figure \ref{interprocess} shows the design involved in sending a message from one process to another. Lets assume there is a message at a client side process and that process wants to send this message to another process. First the client process sends this message to its \textit{ElementContainer}. \textit{ElementContainer} holds all the streams (this is an abstraction of a link in the process graph) to which this message needs to send and it push the message to all streams. Stream decides which node to send this message and passes the message along the target node details to \textit{ConnectionManager} which holds \textit{ClientConnection}s for each node. \textit{ConnectionManager} sends message to correct \textit{ClientConnection} using target node. \textit{ClientConnection} picks an available \textit{DataOutput} from its pool of \textit{DataOutputs} and invokes the serialize method of the message to send that to server side.

### 2014-11-04 paper/system_overview.tex
adding some fixes

\section{System Overview}
Our system mainly consists of a set of processes where each process receives events, processes them and forwards to next processes. We use the term adapters for special processes which receive events from outside systems. These processes and adapters form a graph which represents the way a given event stream is processed within the system. Our current implementation does not support fault tolerance and has adapted topology concept from twitter storm\cite{twitterStorm} and cluster concept from Yahoo S4\cite{neumeyer2010s4}. Rest of this section further describes this concept at a user level. In the next section we provide a detailed explanation about how we have made this inter-process communication efficient. 
\subsection{Process Graph}
A Process graph (Figure \ref{processgraph}) mainly consists of the adapters, processes which execute the processing logic and their interaction patterns. Adapters receive events from outside systems and forward them to other processes. Processes process events according to a given logic and emit the generated events either to other processes or to outside systems.

@@

\subsection{Runtime Graph}
When the system is deployed, there can be many instances of one process to handle higher loads making system scalable. Figure \ref{runtimegraph} shows possible runtime graph for above process graph. Here each parent process instance sends events to two child process instances. However in this case parent process instance has to pick a child process instance to send the message as well. One way of handling this problem is to pick a random node. Other way is to send messages with same key to same child process instance.

@@

\subsection{API}
In this section, we explain our API which can be used to define custom events, processes and adapters. We provide clear interfaces to abstract out all the communication complexities from application developers. Table \ref{api} shows details of client interfaces.

@@

 The Event interface has a method to get the key for a given event. This key is used in sending messages to next processes as described earlier. Parse and serialize methods of event interface are used to directly serialize the event attributes to underlying streams. When implementing these methods developers can define attribute serialization order in serialize method and use the same order at the parse method to avoid metadata passing with the binary format. Processor interface contains a method called onEvent which is invoked by the underlying framework when it receives an event to that process. The start method of the Adapter interface is invoked by the framework and that can be used to pull events from outside systems once the system starts. At the initialization time both processes and adapters receive the container which can be used to send events to other processes.

@@

As shown in Figure \ref{deployment}, a deployment of the system consists of a manager node and a set of worker nodes. Worker nodes are grouped into clusters so that the application users can specify to which clusters each processes needs to get deployed. Manager node process applications, deploy them to worker nodes and initiate the processing by starting the adapters.

>>>>

\section{System Overview}
Our system mainly consists of a set of processes where each process receives events, processes them and forwards them to the next stage. We use the term adapters for special processes that receive events from external systems. These processes and adapters form a graph, which represents how a particular event stream is processed within the system. Our current implementation does not support fault tolerance and has adapted topology concept from Twitter Storm \cite{twitterStorm} and cluster concept from Yahoo S4\cite{neumeyer2010s4}. Rest of this section further describes this concept at a user level. In the next section we provide a detailed explanation about how we have made this inter-process communication efficient. 
\subsection{Process Graph}
A Process graph (Figure \ref{processgraph}) mainly consists of adapters, processes that execute the processing logic, and their interaction patterns. Adapters receive events from external systems and forward them to other processes. Processes process events according to a given logic and emit the generated events either to other processes or to outside systems.

@@

\subsection{Runtime Graph}
When the system is deployed, there can be multiple instances of a particular stage to handle higher loads making the system scalable. Figure \ref{runtimegraph} shows possible runtime graph for above process graph. Here each parent process instance sends events to two child process instances. However in this case parent process instance has to pick a child process instance to send the message as well. One way of handling this problem is to pick a random node. Another approach is to send messages with same key to same child process instance.

@@

\subsection{API}
In this section, we explain our API that can be used to define custom events, processes and adapters. We provide clear interfaces to abstract out all the communication complexities from application developers. Table \ref{api} shows details of client interfaces.

@@

 The \texttt{Event} interface has a method to get the key for a given event. This key is used in sending messages to next processes as described earlier. \texttt{Parse} and \texttt{serialize} methods of \texttt{Event} interface are used to directly serialize the event attributes to underlying streams. When implementing these methods developers can define attribute serialization order in their \texttt{serialize} method and use the same order during \texttt{parse} method to avoid metadata passing with the binary format. \texttt{Processor} interface contains a method called \texttt{onEvent} which is invoked by the underlying framework when it receives an event to that process. The \texttt{start} method of the \texttt{Adapter} interface is invoked by the framework and that can be used to pull events from external systems once the system starts. During initialization both processes and adapters receive the container that can be used to send events to other processes.

@@

As shown in Figure \ref{deployment}, a deployment of the system consists of a manager node and a set of worker nodes. Worker nodes are grouped into clusters so that the application users can specify to which clusters each processes needs to get deployed. The Manager node processes applications, deploys them to worker nodes, and initiates the processing by starting the adapters.
